### 2018-09-17 README.Rmd
updated readme

A comparison of single-cell trajectory inference methods: towards more accurate and robust tools  
Wouter Saelens\*, Robrecht Cannoodt\*, Helena Todorov, Yvan Saeys  
bioRxiv 276907; doi: https://doi.org/10.1101/276907

@@

Based on the results of the benchmark, we provide context-dependent user guidelines. If you want to run methods based on these guidelines, see the [dynorepository](https://github.com/dynverse/dyno). For the guidelines itself, see the [dynguidelines ](https://github.com/dynverse/dynguidelines).

>>>>

> A comparison of single-cell trajectory inference methods: towards more accurate and robust tools  
<strong> Wouter Saelens\* </strong> <a href='https://orcid.org/0000-0002-7114-6248'><img src='https://github.com/dynverse/dynmethods/raw/master/man/figures/orcid_logo.svg' height='16'></a> <a href='https://github.com/zouter'><img src='https://github.com/dynverse/dynmethods/raw/master/man/figures/github_logo.png' height='16'></a>,
<strong> Robrecht Cannoodt\* </strong> <a href='https://orcid.org/0000-0003-3641-729X'><img src='https://github.com/dynverse/dynmethods/raw/master/man/figures/orcid_logo.svg' height='16'></a> <a href='https://github.com/rcannood'><img src='https://github.com/dynverse/dynmethods/raw/master/man/figures/github_logo.png' height='16'></a>,
Helena Todorov <a href='https://github.com/Helena-todd'><img src='https://github.com/dynverse/dynmethods/raw/master/man/figures/github_logo.png' height='16'></a>,
<em> Yvan Saeys </em> <a href='https://github.com/saeyslab'><img src='https://github.com/dynverse/dynmethods/raw/master/man/figures/github_logo.png' height='16'></a>  
[bioRxiv:276907](https://www.biorxiv.org/content/early/2018/03/05/276907) [doi:10.1101/276907](https://doi.org/10.1101/276907)

@@

Based on the results of the benchmark, we provide context-dependent user guidelines, [available as a shiny app](https://github.com/dynverse/dynguidelines). This app is integrated within the [dyno pipeline](https://github.com/dynverse/dyno), which also includes the wrappers used in the benchmarking and other packages for visualising and interpreting the results.

![dynguidelines](https://github.com/dynverse/dynguidelines/raw/master/man/figures/demo.gif)
